---
author:
  - name: Asst. Prof. Fabio A. CRUZ SANCHEZ
    affiliation:
      - name: Université de Lorraine
        department:  ENSGSI
        address: 8 rue Bastien Lepage
        city: Nancy
        country: France
        postal-code: 54000
address:
  - Dear **Cédric Cabanne**
  - Project Officer at the European Education and CultureExecutive Agency (EACEA) of the European Commission

subject-title: "Subject"
subject: "**Amendment requested by the TechTraPlastiCE consortium**"
opening: "Dear Project Officer:"
closing: "Yours Faithfully,"

fontsize: 12pt
format:
  letter-pdf:
    output-file: index
    include-in-header: [../../assets/TTPLCE-packages.tex]
    keep-tex: false
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.retina = 3, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')

library(tidyverse)
library(kableExtra)
library(readxl)
library(here)

```


\thispagestyle{fancy}

Since February 2025, the TechTraPlastiCE consortium has been working to strengthen the applied research and technology transfer capacities of Higher Education Institutions (HEIs) in Argentina, Colombia, and Chile. 
The project aims to enhance the service portfolios of participating institutions and support the green transition towards a circular economy within the plastics value chain.
Following the initial implementation phase of the project, the consortium has identified a number of adjustments that are necessary to ensure the successful achievement of the project's objectives and to improve the coherence between the planned activities and the expected deliverables.

On behalf of the TechTraPlastiCE consortium, we therefore kindly request an amendment (AT21) to Grant Agreement No. 101179564 concerning the Description of the Action (DoA), specifically the modifications related to Work Package 3, "*Multi-actor Collaborations for a Just and Safe Plastic Circular Economy*".
The current list of WP3 deliverables is presented in @tbl-link, while the proposed modifications are presented in @tbl-changes.

The requested changes are as follows:

1. **Deliverable D3.1**:
   - Change of title from "Interviews Reports" to "Comprehensive Problem Definition on the Reuse Challenge".
   - Change of lead beneficiary from COLUMBUS to PUCV.
   - Due date: 31 October 2026.

1. **New Deliverable D3.2**:
   - Addition of a complementary deliverable entitled "Report on Contacts and Results of Interviews".
   - Lead beneficiary: COLUMBUS.
   - Due date: 30 November 2026.

1. **Deliverable D3.3**:
   - Change of due date from 31 October 2026 to 30 November 2026.
1. **Deliverable D3.4**:
   - Change of title from "5 Events Reports (1 per country)" to "Search Conference Reports".
   - Change of due date from 31 January 2027 to 30 June 2027.
1. **Deliverable D3.5**:
   - Change of due date from 31 January 2027 to 31 August 2027.



The reasons for these proposed modifications are detailed below.

1. **Deliverable D3.1**

The revised title more accurately reflects the actual content of the deliverable, which goes beyond reporting interview outcomes and instead provides a comprehensive definition of the reuse challenge identified through stakeholder engagement and analysis. Furthermore, assigning PUCV as the lead beneficiary better reflects the distribution of expertise and responsibilities within the consortium, as PUCV is leading the scientific work related to this activity.

2. **New Deliverable D3.2**

The introduction of Deliverable D3.2 aims to preserve the documentation initially foreseen under D3.1 by providing a dedicated report on stakeholder contacts and interview results for the planifacation of the Search Conferences methodology for participative planning. Separating these outputs will improve the clarity of the project's deliverables while ensuring that both the interview process and the resulting problem definition are adequately documented. This report will also provide the necessary evidence base for the preparation and implementation of the Search Conference methodology across the participating HEIs.

3. **Deliverable D3.3**

The benchmarking study requires additional time to collect, analyse and synthesise information from multiple countries and institutions. Extending the deadline by one month will ensure a more comprehensive analysis and produce results that will better support the subsequent activities of Work Package 3.

4. **Deliverable D3.4**

The proposed title better reflects the activities described in the Description of the Action. As indicated in the DoA, four Search Conferences are planned to be organised at the participating Higher Education Institutions: Pontificia Universidad Católica de Valparaíso --PUCV-- (Chile), Universidad Central --UC-- (Colombia), Universidad Nacional de Córdoba --UNC-- (Argentina), and Universidad Nacional de Río Negro --UNRN-- (Argentina).
The previous title referring to "5 Events Reports" does not accurately represent the planned activity. The revised title therefore corrects this inconsistency and better aligns the deliverable with the approved project methodology.

In addition, organising the Search Conferences requires extensive coordination with external stakeholders representing the plastics value chain in each country. 
Scheduling these participatory workshops depends on the availability of numerous socio-economic actors and therefore involves factors that cannot be fully controlled by the consortium.
For this reason, the consortium proposes extending the deadline to 30 June 2027. 
This additional time will ensure that all Search Conferences are successfully organised, their outcomes are properly documented, and the resulting action plans can effectively support the implementation of Work Package 4.

These modifications do not affect the objectives, methodology, or expected impact of Work Package 3, nor do they compromise the overall objectives or implementation of the TechTraPlastiCE project.

5. **Deliverable D3.5**: 

The updated institutional portfolios are directly dependent on the outcomes of the Search Conferences. Since the completion of these conferences is proposed for June 2027, extending the deadline for Deliverable D3.5 to 31 August 2027 will provide sufficient time for each participating university to integrate the agreed initiatives into its portfolio and produce a high-quality final deliverable.

In conclusion, the proposed amendments are intended to improve the consistency between the Description of the Action and the actual implementation of Work Package 3, while ensuring the quality, relevance, and practical impact of its deliverables. 
The consortium remains fully committed to achieving the objectives of the TechTraPlastiCE project and believes that these adjustments will strengthen its overall implementation without affecting its expected outcomes.

We kindly ask for your consideration of this amendment request and remain at your disposal should you require any additional information or clarification.

Thank you for your continued support and cooperation.

Yours sincerely,

On behalf of the TechTraPlastiCE Consortium



\begin{textblock}{10}(9,19)
  \fontsize{11}{8}
  \selectfont \sffamily
  \color[gray]{0.4}
  \begin{tabular}{@{}l@{}}
    \hline \\
    Asst. Prof. \textbf{Fabio A. CRUZ SANCHEZ} \\
    8 rue Bastien Lepage,  54000 Nancy \\[0.15cm]
    \faIcon{envelope} \href{mailto:fabio.cruz@univ-lorraine.fr}{fabio.cruz@univ-lorraine.fr} \\
    \faIcon{phone} +33 3 72 74 35 31 \\
    \faIcon{house}  \href{https://ensgsi.univ-lorraine.fr/}{https://ensgsi.univ-lorraine.fr/}
  \end{tabular}
\end{textblock}


:::landscape

```{r}
#| label: tbl-link
#| tbl-cap: "Current Deliverables of WP3."
#| tbl-pos: H

table <- 
tribble(
~"Del.",
~"Name",
~"Description",
~"Lead Beneficiary",
~"Dissemination Level",
~"Due Date",

"D3.1",	
"Interviews reports",	
"Based on provided guidelines, partners that will implement the Search Conferences methodology will conform interdisciplinary staff and researchers to prepare one-on-one conversations with defined actors (industries, social and economic actors involved in the reuse challenge, to explore in depth the leverage, and provide together a more comprehensive problems definition. All these conversations will need to be reported  in a document file",	
"COLUMBUS",
"SEN", 
"31 Oct 2026",

"D3.2",
"Benchmarking study",
"The identified problems involving multi-actors visions and roles are foreseen to be problems that are also faced in other countries and cities. The benchmarking will help to find inspiration in how similar multilevel problems have been approached to start identifying clues of actions. 
The benchmarking study will be structured as a public document available for all the partners",	
"PUCV",
"PU",
"31 Oct 2026",

"D3.3",
"5 events reports (1 per country)",
"Each search conference will deliver a report containing the results of the 1-day event, the number of participants, the minutes of the encounter, and especially the specific solutions/projects identified among the multi-actors participants and the University.",	
"COLUMBUS",
"SEN",
"31 Jan 2027",

"D3.4",	
"Updated portfolios",
"Updated portfolios	Universities will update the defined portfolios with the new social-multi actors initiatives that were identified and prioritized during the search conference event. The portfolio will be available in the repository.",	
"UNS",
"PU",
"31 Jan 2027"
)



table %>%
  mutate_all(linebreak) %>%
  kbl("latex", booktabs = T, escape = F, 
      longtable = T, 
      linesep = "\\midrule\\addlinespace") %>%
   kable_styling(full_width = F, 
                latex_options = c("repeat_header"),                
                font_size = 11) %>% 
   row_spec(0, color = "white", background = "Naranja", bold = T, font_size = 9) %>%
   column_spec(1, width = c("1cm"))  %>%
   column_spec(2, width = c("2cm"))  %>%
   column_spec(3, width = c("10cm"))  %>%
   column_spec(4, width = c("2cm")) %>%
   column_spec(5, width = c("2cm")) %>%
   column_spec(6, width = c("1cm"))  
```



```{r}
#| label: tbl-changes
#| tbl-cap: "Proposed changes on the WP3."
#| tbl-pos: H

table <- 
tribble(
~"Del.",
~"Name",
~"Description",
~"Lead Beneficiary",
~"Dis. Level",
~"Due Date",

"D3.1",
"Comprensive problem definition on the reuse challenge",
"Based on provided guidelines, partners that will implement the Search Conferences methodology will conform interdisciplinary staff and researchers to prepare one-on-one conversations with defined actors (industries, social and economic actors) involved in the reuse challenge, to explore in depth the leverage, and provide together a more comprehensive problems definition. All these conversations will need to be reported  in a document file.", 
"PUCV",
"PU", 
"31 Oct 2026",

"D3.2",
"Report on contacts and results of interviews",
"The universities where the Search Conferences will be held will have identified and contacted the most relevant organisations to participate in the Search Conferences. The aim is to identify their points of interest, pre-identify concrete initiatives and engage the participation of decision-makers.",
"COLUMBUS",
"SEN",
"28 Fev 2027",

"D3.3",
"Benchmarking study",
"The identified problems involving multi-actors visions and roles are foreseen to be problems that are also faced in other countries and cities. The benchmarking will help to find inspiration in how similar multilevel problems have been approached to start identifying clues of actions. The benchmarking study will be structured as a public document available for all the partners.",
"COLUMBUS",
"PU",
"30 Nov 2026",

"D3.4",
"Search conference reports",
"There will be four Search Conferences for TechTraPlastiCE project. Two in Argentina leaded by UNRN, UNC. One in Colombia lead by UC and one in Chile lead by PUCV. Each search conference will deliver a report containing the results of the 1-day event, the number of participants, the minutes of the encounter, and especially the specific solutions/projects identified among the multi-actors participants and the University.",	
"COLUMBUS",
"SEN",
"30 June 2027",

"D3.5",	
"Updated portfolios",
"Universities will update the defined portfolios with the new social-multi actors initiatives that were identified and prioritized during the search conference event. The portfolio will be available in the repository.",	
"UNS",
"PU",
"31 August 2027"
)

table %>%
  mutate_all(linebreak) %>%
  kbl("latex", booktabs = T, escape = F, 
      longtable = T, 
      linesep = "\\midrule\\addlinespace") %>%
   kable_styling(full_width = F, 
                latex_options = c("repeat_header"),                
                font_size = 11) %>% 
   row_spec(0, color = "white", background = "Naranja", bold = T, font_size = 9) %>%
   row_spec(2, color = "Naranja" ) %>%
   column_spec(1, width = c("1cm") )  %>%
   column_spec(2, width = c("2.5cm"), color = c("Naranja", "Naranja", "black", "Naranja", "black"))  %>%
   column_spec(3, width = c("13cm"), color = c("black", "Naranja", "black", "Naranja", "black"))  %>%
   column_spec(4, width = c("2cm")) %>%
   column_spec(5, width = c("1cm")) %>%
   column_spec(6, width = c("1cm"), color = c("black", "Naranja", "Naranja", "Naranja", "Naranja"))  
```

:::



\includepdf[landscape=true, scale=1, pages=-]{../../assets/Gantt/_Gantt.pdf}
